\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage[scale=0.75]{geometry}
\usepackage{graphicx, txfonts}

\date{\today}

%====================%
%=======Header=======%
%====================%
\firstname{Iman}
\familyname{Tabrizian}

\title{Curriculum Vitae}
\begin{document}

\makecvtitle

%=========================%
%=======ContactInfo=======%
%=========================%
\section {Contact Info}

\cvitem{Email}{ Tabrizian@aut.ac.ir}

\cvitem{Mobile}{+989377371367}
\cvitem{Github}{\href{https://github.com/tabrizian}{github.com/tabrizian}}
\cvitem{StackOverflow}{\href{http://stackoverflow.com/users/4453461/iman}{http://stackoverflow.com/users/4453461/iman}}

\section{Research Interests}
\cvlistitem{Internet of Things (IoT)}
\cvlistitem{Computer Networks}
\cvlistitem{Distributed Systems}
\section{Education}

\cventry{2014--2018 (Expected)}{Undergraduate, Computer Software Engineering}
{ Amirkabir University of Technology}{ Tehran}{ Iran}{
    \begin{itemize}
        \item Current GPA 18.44 / 20 (68 / 144 credits) \\
    \end{itemize}
}

\cventry{2010--2014}{Diploma of mathematics and physics}{Rouzbeh High School}{Tehran}{Iran}{
    \begin{itemize}
        \item GPA 19.34 / 20 \\
    \end{itemize}
}


%=========================%
%=========Honors==========%
%=========================%
\section{Honors}

\cvitem{2015}{Eligible to choose a second major due to outstanding performance.}
\cvitem{2015}{Chosen as finalists at $7^{th}$ Java Challenge. (As a member of our team)}
\cvitem{2015}{Participated in the $16^{th}$ ACM-ICPC of West Asia, Sharif University of Technology, Tehran, Iran.}
\cvitem{2015}{Ranked $1^{st}$ among undergraduate students of Computer Engineering, 2014 beginners, $14^{th}$ ACM-ICPC, Amirkabir University of technology.}
\cvitem{2012}{Accepted in the first phase of the Computer and Mathematics National Olympiad.}

\section{Public Speaking}

\cventry{2016}{Presenter at 8th National Linux Festival}{Amirkabir University of Technology}{Tehran}{Iran}{}

\section{Work Experience}
\cventry{2016--current}{Member of the IoT labratory}{Amirkabir University of Technology}{Tehran}{Iran}{
Creation of middleware to work with different hardware actuators and sensors,
and providing RESTful services for working with application services and analysis.
Source code and more info is available at here \href{https://github.com/AoLab/I1820}{https://github.com/AoLab/I1820}}

\cventry{2016--current}{Software developer }{Farzan Fanandish Farda}{Tehran}{Iran}{
Creation of a web-based software that provides APIs for fetching data from the
250 welding robots for Iran Khodro (A car producing company in Iran) and sending
weld commands for them.}

\cvitem{Summer 2016}{Internship at DATAX company, Fanap Holding Group}


\section{ Teaching Experience}
\cvitem{2016}{ Teaching Assistant, Advanced Programming,
    Amirkabir University of Technology, Under supervision of
    Prof. Noorhosseini}
\cvitem{2015}{ Teaching Assistant, Introduction to Programming, Amirkabir
    University of Technology, Under supervision of Prof. Bakhshi}
\cvitem{2014--2015}{ Teacher, Introduction to programming with C++,
    Rouzbeh High school, 4 semesters.}

\section{Projects - Mostly Available on github.com/tabrizian}

\cvitem{2016}{Providing a middleware for connecting series of sensors and
    actuators with different protocols to the internet. \textbf{Python} $\to$
    \href{https://github.com/AoLab/I1820}{link}}

\cvitem{2016}{Creation of \textit{NovinNet} application for networking 250
    welding robots for Iran Khodro. \textbf{PHP Laravel} $\to$
    \href{https://git.imantabrizian.me/tabrizian/NovinNet}{link}}

\cvitem{2016}{Goldoon - Project for monotring flowers humidity using nodemcu
    and RPi. \textbf{C++, NodeJS} $\to$
    \href{https://github.com/tabrizian/Goldoon}{link}}

\cvitem{2015-2016}{Iran Metro - An application for timetables and facilities
    of the metro station. Honored as the SELECTED NEW APP OF THE WEEK by cafebazaar
    (Iranian Android Market) \textbf{Java Android} $\to$
    \href{http://cafebazaar.ir/app/ir.blog.chameco.iranmetro/?l=en}{link}}

\cvitem{2015}{RoboKill Implementation of RoboKill game \textbf{Java} $\to$
    \href{https://github.com/tabrizian/RoboKill}{link}}

\cvitem{2015}{Implementation of a simple guessing game, this was also executed
    on AlteraDE2 borad - \textbf{Verilog HDL}
    \href{https://github.com/tabrizian/GuessNumber}{link}}

\section{Skills and Expertise}
    \cventry{$\bullet$}{Web Programming}{}{}{}{PHP, Ruby, HTML, CSS, Javascript, Nodejs, Laravel}
    \cventry{$\bullet$}{General Software Programming}{}{}{}{Matlab, Java, C/C++}
    \cventry{$\bullet$}{Hardware Design Languages}{}{}{}{Verilog, VHDL}

    \cventry{$\bullet$}{Type Setting}{}{}{}{VIM, \LaTeX, LibreOffice, Microsoft Word}

    \cventry{$\bullet$}{Hardware Simulators}{}{}{}{ModelSim, Quartuas, GHDL}

    \cventry{$\bullet$}{DBMS}{}{}{}{MySQL, MongoDB, SQLite, SQL Server}

    \cventry{$\bullet$}{Operating Systems}{}{}{}{Microsoft Windows, Linux (Ubuntu), Raspbian}

    \cventry{$\bullet$}{IDE}{}{}{}{Eclipse, Android Studio, IntelliJ IDEA, CLion, PHPStorm}

    \cventry{$\bullet$}{Commandline tools}{}{}{}{}

    \cventry{$\bullet$}{Build Automations}{}{}{}{Makefile, Gradle, Maven, CMake}

    \cventry{$\bullet$}{Misc}{}{}{}{Docker - see \href{https://hub.docker.com/u/tabrizian/}{hub.docker.com/u/tabrizian/}}

\section{ Undergraduate courses}
    \cventry{$\bullet$}{Introduction to Programming}{}{}{}{19.5 / 20}
    \cventry{$\bullet$}{Advanced Programming with Java}{}{}{}{20 / 20}
    \cventry{$\bullet$}{Data structures and algorithms}{}{}{}{20 / 20}
    \cventry{$\bullet$}{Digital systems design}{}{}{}{17.5 / 20}
    \cventry{$\bullet$}{Electrical circuits}{}{}{}{19.54 / 20}
    \cventry{$\bullet$}{Engineering Statistics}{}{}{}{19.7 /20}
    \cventry{$\bullet$}{Algorithm Design}{}{}{}{20 / 20}
    \cventry{$\bullet$}{Principles of database design}{}{}{}{17.7 / 20}
    \cventry{$\bullet$}{Theory of machines and languages}{}{}{}{18.5 / 20}
\section{ Languages}
\begin{itemize}
    \item Persian (Native Proficiency)
    \item English (Professional Working proficiency)
\end{itemize}
\section{ Refrences}
References available upon request
\end{document}
